Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
fix AP restriction text

\textbf{Alert production is restricted -- }
User-Generated Processing will not be able to release alert packets in the LSST alert stream.
As the latency on processed visit image availability has an 80-hour
embargo, no user-generated pipeline will be able to process Special Programs 
data on a timescale similar to prompt processing and alert production 
(60 seconds to 24 hours).
Thus, no User-Generated Processing may contribute alerts to the LSST alert stream on 
any timescale.

>>>>

\textbf{Alert production is restricted -- }
As processed visit images will embargoed for 80 hours,
only official Rubin Prompt processing may produce alerts.
No User-Generated Processing may contribute alerts to the LSST alert stream.
